---
title: "Week 1 Exercise Part B"
author: "fruggli"
format: html
editor: visual
---

```{r}
#| label: load-packages
#| include: false

library("MASS")
library(tidyverse)
set.seed(42)
```

## Samples

In the first step we are creating 100 samples with a negative binomial distribution ( mu=10, dispersion=2, using the parameterisation with mean=mu and variance=mu+mu\^2\*dispersion). We are using a seed to make the data reproducible.

```{r}

negbin_data <- rnegbin(100, mu = 10, theta = 2)

log_data <- log(negbin_data)

mean_dat <- mean(negbin_data)
var_dat <- var(negbin_data)

```

## Histogram of sampled data

In the next step we are visualizing the samples in two histogram plots. In the first one with a linear scale and the second one with a log scale.

```{r}
#| echo: false
par(mfrow = c(1,2))

hist(negbin_data, main = 'Histogram of sampled data')
hist(log_data, main = 'Histogram of log scaled data')
```

## Mean and Variance of the data

The mean and variance of the sampled data are:

```{r}
#| echo: false

print(paste("Mean:", mean_dat))
print(paste("Variance:", var_dat))
```
